Keystoneness, centrality, and the structural controllability of ecological networks

### 2019-01-16 paper/manuscript.Rmd
Improve clarification of random effects in main text

\R{R2-one-lumped-model-a}We then examined how species-level properties were related to control capacity using a set of candidate generalised linear models with binomial error structure. 
These models included five predictor variables that mirror the network-level predictors. 
First, the species' contribution to nestedness, which has been proposed as a key feature that promotes stability and robustness in mutualistic networks [@saavedra_strong_2011]. 
Second,\R{R2-species-strength-a} the species' strength (the sum of a species' visits), which quantifies the strength of a species' associations and is indirectly related to its abundance [@poisot_comparative_2012]. 
Third, the direction of asymmetry which quantifies the net balance in dependencies; that is, it indicates if a species affects other species more than what they affect it or not [@vazquez_species_2007]. 
Fourth, the species' degree in order to account for the intrinsic centrality of a species.
Finally, we included a categorical variable for the species' trophic level (plant or pollinator) and an interaction term between trophic level and the previous four variables. 
To facilitate comparison between predictors, degree and visitation strength were log-transformed and all four continuous variables were scaled to have a mean of zero and a standard deviation of one. 
\R{R2-one-lumped-model-b}In these models, species from all networks were analysed together. 
\R{R2-random-effects}We initially included random effects to account for possible variation across communities, but we found that the among-group variance was effectively zero, and therefore random effects were not included in further analyses. 
\R{R2-all-candidates}We then generated all possible candidate models across the space of models with all, some, and none of the predictor variables.
To identify the models that were best supported by the data, we first determined the most parsimonious random structure using the AICc. 
The relative importance of variables was then assessed by looking at their effect sizes in the top-ranked models and the cumulative weight of the models in which they are present.

>>>>

\R{R2-one-lumped-model-a}We then examined how species-level properties were related to control capacity using a set of candidate generalised linear models with binomial error structure. 
These models included five predictor variables that mirror the network-level predictors. 
First, the species' contribution to nestedness, which has been proposed as a key feature that promotes stability and robustness in mutualistic networks [@saavedra_strong_2011]. 
Second,\R{R2-species-strength-a} the species' strength (the sum of a species' visits), which quantifies the strength of a species' associations and is indirectly related to its abundance [@poisot_comparative_2012]. 
Third, the direction of asymmetry which quantifies the net balance in dependencies; that is, it indicates if a species affects other species more than what they affect it or not [@vazquez_species_2007]. 
Fourth, the species' degree in order to account for the intrinsic centrality of a species.
Finally, we included a categorical variable for the species' trophic level (plant or pollinator) and an interaction term between trophic level and the previous four variables. 
To facilitate comparison between predictors, degree and visitation strength were log-transformed and all four continuous variables were scaled to have a mean of zero and a standard deviation of one. 
\R{R2-one-lumped-model-b}In these models, species from all networks were analysed together. 
\R{R2-random-effects}We initially included random effects to account for possible variation across communities. 
Specifically, we tested structures that allowed for a random intercept for the network, site, and the study it comes from.
However, we found that in all cases the among-group variance was effectively zero, and therefore we did not include any random effect in further analyses. 
\R{R2-all-candidates}We then generated all possible candidate models across the space of models with all, some, and none of the predictor variables.
To identify the models that were best supported by the data, we first determined the most parsimonious random structure using the AICc. 
The relative importance of variables was then assessed by looking at their effect sizes in the top-ranked models and the cumulative weight of the models in which they are present.
